Orchestrating stencils with the Multi-Stencil Framework

### 2017-03-02 ARTICLES/IJPP/articleR1/msf.tex
Section 2.2

Figure~\ref{fig:msf} presents the overview of the Multi-Stencil Framework that will be entirely detailed throughout this paper. It is composed of four different parts presented below.
One can note in this figure that MSF is addressed to two different kinds of end-users: the \emph{numerician}, in other words the mathematician, and the \emph{developer}. Most of the time numericians do have programming knowledge, however as it is not their core domain and because of a lack of time, development is often left to engineers according to numericians needs. MSF has the interesting particularity to propose a clear separation of concerns between these two end-users by distinguishing the description language from the numerical code.

MSF also has the interesting capability to be more flexible than existing solutions thanks to a possibility for a third party to interact with the framework. This third party is a High Performance Computing (HPC) specialist as illustrated in Fig.~\ref{fig:msf}.

@@

\paragraph{\textbf{Multi-Stencil Compiler}}
The core of the framework is the Multi-Stencil Compiler, or MSC. It is responsible for transforming the genric assembly into the final parallel assembly which is specific to the simulation described by the numerician with MSL. MSC is described in Section~\ref{sect:parallelism}.

\paragraph{\textbf{Specialized assembly}}
Finally, the output of MSF is the component assembly generated by MSC. It is an instanciation and a transformation of the generic component assembly, by adding component types, transforming some part of the assembly, and by adding specific components generated by MSC. From this final component assembly which is specific to the simulation initially described with MSL, the developer will finally write numerical codes. This final specialized component assembly represents the parallel computations orchestration of the simulation initially described by the numerician.

>>>>

Figure~\ref{fig:msf} gives an overview of the Multi-Stencil Framework that is entirely detailed throughout this paper. It is composed of four distinct parts described hereafter.
As illustrated in Figure~\ref{fig:msf}, MSF targets two different kinds of end-users: the \emph{numerician}, in other words the mathematician, and the \emph{developer}. Most of the time numericians do have programming knowledge, however as it is not their core domain and because of a lack of time, development is often left to engineers according to numerician needs. MSF has the interesting particularity to propose a clear separation of concerns between these two end-users by distinguishing the description language from the numerical code. \CP{pas top clair la fin de la phrase}

MSF also has the interesting capability to be more flexible than existing solutions thanks to a possibility for a third party to interact with the framework. This third party is a High Performance Computing (HPC) specialist as displayed in Figure~\ref{fig:msf}.

@@

\paragraph{\textbf{Multi-Stencil Compiler}}
The core of the framework is the Multi-Stencil Compiler, or MSC. It is responsible for transforming the generic assembly into the final parallel assembly which is specific to the simulation described by the numerician with MSL. MSC is described in Section~\ref{sect:parallelism}.

\paragraph{\textbf{Specialized assembly}}
Finally, the output of MSF is the component assembly generated by MSC. It is an instanciation and a transformation of the generic component assembly, by adding component types, transforming some part of the assembly, and by adding specific components generated by MSC. From this final component assembly which is specific to the simulation initially described with MSL, the developer will finally write numerical codes. This final specialized component assembly represents the parallel computations orchestration of the simulation initially described by the numerician.
\CP{Dire que c'est du \llc?}
